Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-06-22 Latex/rebuttal.txt

 
> Manuscript Number: OPHOTO-D-21-00020  
> Towards Spherical Robots For Mobile Mapping In Human Made
> Environments
>
> Dear Mr. Bredenbeck,     
> 
> Thank you for submitting your manuscript to ISPRS Open Journal of
> Photogrammetry and Remote Sensing.
>

> I have completed my evaluation of your manuscript. The reviewers
> recommend reconsideration of your manuscript following revision. I
> invite you to resubmit your manuscript after addressing the comments
> below. Please resubmit your revised manuscript by Jul 13, 2021.  
> When revising your manuscript, please consider all issues mentioned
> in the reviewers' comments carefully: please outline in a cover
> letter every change made in response to their comments and provide
> suitable rebuttals for any comments not addressed. Please note that
> your revised submission may need to be re-reviewed.     
> 
> To submit your revised manuscript, please log in as an author at
> https://www.editorialmanager.com/ophoto/, and navigate to the
> "Submissions Needing Revision" folder under the Author Main Menu.
> 
> ISPRS Open Journal of Photogrammetry and Remote Sensing values your
> contribution and I look forward to receiving your revised
> manuscript.
>   
> Kind regards,     
> 
> George Vosselman   
> Editor-in-Chief   
> ISPRS Open Journal of Photogrammetry and Remote Sensing    
>  
> Editor and Reviewer Comments:     
> 
> Editor:
> As you will see below both reviewers appreciate your work and don't
> have concerns regarding the methodology or results. Reviewers, in
> particular Reviewer 2, however, do have a large number of
> recommendations to improve the readability of your manuscript. Given
> the number of recommendations, I ask for a major revision. The
> recommendations should, however, be easy to implement.
>  
>   
> Reviewer 1: The manuscript presents the concept of a spherical
> mobile mapping system, and a data registration method utilizing the
> geometric constraints available in human-made environments,
> e.g. planar surfaces.
> 
> The manuscript has novel content and is well written, and can be
> accepted after minor revision. My comments and suggestions to be
> considered by the authors are as follows:
> 
> Lines 27-31: Spherical shell can protect the sensors inside, but
> this does not prevent the external disturbances such as dust or
> other impurity staining the sphere itself, affecting the performance
> of the system. So in principle this does not change the situation
> from using protective covers on "traditional" mobile mapping
> systems.
> 
> Lines 111-116: Modern kinematic scanning systems collect point cloud
> data with high speed, so also kinematic point clouds are often dense
> enough for robust plane determination. And on the other hand, sparse
> point clouds are not optimal for point-to-point matching due to the
> long distances between adjacent points.
> 
> Lines 244-246: The Livox ranging precision is given twice in this
> sentence.
> 
> Figure 4: The x-scale is given in figure caption, but I would
> suggest adding it to the figure also.
> 
> Conclusion: Whereas the title, Abstract and Introduction concentrate
> mostly on the spherical mobile mapping, Conclusion deals almost
> entirely with the topic of registration, thus feeling somewhat
> separated from the rest of the manuscript. Reading the Conclusion,
> one could not expect that the title of the manuscript is "Towards
> Spherical Robots For Mobile Mapping In Human Made Environments".
> 
> 
> 
> 
> 
> Reviewer 2: The authors have written a very interesting paper on the
> topic of mobile mapping with a spherical robot in human-made
> environments. In a rather slim paper and pleasantly concise form,
> they present their approach and show first results based on
> simulated and real measurement data. The reading flow is mostly
> pleasant and no irrelevant information is given. Conversely, the
> authors leave out important details in several places, which would
> be very helpful for the reader's understanding. In the following,
> there are several points for improvement and critical questions that
> should be taken into account by the authors. Due to the large number
> and the importance of central points, I recommend a major revision.
> 
> - A short outline at the end of the introduction is missing and
> would give the reader a better overview of the further content and
> should therefore be added.
> 
> - In the entire article, no reference is made to the targeted or
> required accuracy potential with regard to the quality of the pose
> determination and the final point cloud, which in my view requires
> at least a rough classification.
> 
> - For the short state of the art of existing mobile systems, which
> is mainly based on the authors' own systems, in my opinion, at least
> the NavVis VLX system could be added, which in comparison is newer
> and as a human-operated system for mapping is one of the benchmarks.
> 
> - The authors mention unknown and dangerous environments as a
> possible field of application, in which the advantages of the
> spherical system should come into play. However, only one space
> application is mentioned as a specific example, which may be valid
> in itself, but does not fit the topic of the paper very
> well. Application scenarios should therefore be supplemented by
> terrestrial areas and in particular by human-made environments,
> which better motivate the future use and justification of such
> systems for the reader.
> 
> - The advantages of a spherical mobile platforms are discussed, but
> nothing is said about possible disadvantages or
> limitations. Moreover, I wonder whether the "unique advantages"
> mentioned in the abstract are really so remarkable. For example,
> what about the recording constellation, which in my view is
> relatively unfavourable on the ground and leads to restricted fields
> of view and weak angles of incidence when mapping the
> ground. Another advantage stated by the authors is that the shell
> protects the sensors, which is reasonable. However, this protection
> is only necessary because you are moving directly on the ground. In
> addition, can dust and dirt accumulate on the outer shell and
> influence the acquisition?
> 
> - Section 2.1 discusses existing laser scanner-based SLAM
> approaches, concluding with the statement (page 2, column 1, line
> 30-33) that all of these approaches do not include the structural
> properties of human-made environments in the calculations. This
> statement is not true. There are a variety of SLAM approaches
> (e.g. Jung et al. 2015; Nguyen et al.  2006), but also other
> applications with recursive state estimation, which make use of this
> additional information in the context of georeferencing. This should
> be investigated and reworked in more detail.
> Jung, J., Yoon, S., Ju, S., and Heo, J. (2015). Development of Kinematic
> 3D Laser Scanning System for Indoor Mapping and As-Built BIM Using
> Constrained SLAM. In: Sensors (Basel, Switzerland), 15(10), DOI:
> https://doi.org/10.3390/s151026430
> Nguyen, V., Harati, A., Martinelli, A., Siegwart, R., and Tomatis, N.
> (2006). Orthogonal SLAM: A Step Toward Lightweight Indoor Autonomous
> Navigation. In: IEEE/RSJ International Conference on Intelligent Robots
> and Systems, DOI: https://doi.org/10.1109/IROS.2006.282527
> 
> - The introduction in Section 3 should be revised as it is not very
> intuitive for the reader and something about the objectives and
> motivation for this section is missing. However, this is also
> directly related to the general lack of outline beforehand.
> 
> - In section 3, the authors introduce their own algorithm for
> registration, but they do not give any further information about the
> temporal context in which this takes place. This is probably done in
> the context of each epoch, although it is also not clear how an
> epoch is defined. Is it a single full rotation of the laser scanner
> or that of the sphere? And does the registration always take place
> only locally in relation from the current epoch to the last epoch or
> with a window approach or even globally?
> 
> - Section 3.2 deals with the extraction of planes, but the following
> questions remain unclear: Are the planes always searched for only in
> the context of the observational data of the current epoch or with
> regard to the already registered global point clouds? How many
> planes are needed at all and what demands are made on their spatial
> distribution? The abstract mentioned parallel and perpendicular
> planes, but this is not discussed further here. Are only these used
> and if so, why? Furthermore, what about planes that are not
> necessarily parallel or perpendicular (e.g. doors, cupboards)? How
> is the flatness of a plane checked? How are outliers dealt with,
> especially with regard to existing measurement and motion noise?
> 
> - Throughout Section 3, numerous variables are not introduced and
> are not explained in more detail, so that a more precise
> interpretation of the individual equations is unfortunately very
> difficult.
> 
> - What orders of magnitude were finally used for the range noise
> model in Section 4.2 and why was this not also done for the angular
> resolution?
> 
> - In the context of the real experiment in Section 5, a major
> simplification is made. Even if this simplification is certainly
> suitable for the beginning, this special case comes quite surprising
> here...especially in comparison to the simulation and the previously
> described topic. Have other measurements not yet been carried out or
> what is the background? At least this simplification should be
> mentioned beforehand, otherwise the reader will have false
> expectations.
> 
> - Wouldn't it also be interesting to compare the estimated pose
> parameters with the nominal values from the simulation within the
> framework of Section 6.1? So far, the focus has only been on the
> point cloud.
> 
> - Why is there no qualitative validation for the results of the real
> data in Section 6.2? A reference scan based on a terrestrial laser
> scanner would be a possibility or otherwise based on the flatness of
> known planes in the registered point cloud?
> 
> - In the Conclusion, the parallelism and perpendicularity within the
> environment is mentioned again, although this did not play a role in
> the main part of the paper. Therefore, the question arises why do
> the planes have to be parallel or perpendicular at all and why is
> this mentioned at the beginning? This is not clear, since no
> additional constraints on this additional information have been
> introduced so far. There are also already other methods available
> that take this idea of geometric constraints for georeferencing into
> account.
> 
> Further open questions/comments are:
> Page 1, Line 15: Double use of "protect", which should be replaced
> by another word.
> Page 1, Line 21: The link for the "second option" to the use of an
> IMU is not necessarily obvious.
> Page 1, Column 2, Line 52-56: Complicated sentence which should be
> reformulated.
> Page 2, Column 2, Line 15: The term "long stop" is not to be
> interpreted clearly in this context. How is "long" defined in this
> sense in terms of time or space?
> Page 3, Column 1, Line 6-8: A specific reference should be given for
> the first half of the sentence, as reference 19 probably only refers
> to the second part.
> Page 3, Column 1, Line 23-26: Not all variables were introduced
> accurately
> Page 3, Column 1, Line 33-34: Selection of references for this?
> Page 3, Column 1, Line 34-35: But what demands are made on the
> assignment? This is unclear to the reader, also in connection with
> the general quality requirements of the whole approach.
> Page 3, Column 1, Line 38: How can the threshold value be specified,
> since it is probably not identical for all applications and
> environments? Later, there is also no indication of the choice of
> the value in the own simulated and real data sets.
> Page 3, Column 1, Line 50: What does the index k describe and what
> is the difference to the index i from Section 3.2?
> Page 3, Equation (1): Again, some variables are not specified. For
> example, the source of tx ty tz is unclear.
> Page 3, Equation (3): Equation unclear regarding the use of the 2 in
> the exponent as well as the index.
> Page 3, Equations (4)-(5): Here I don't understand how to get to the
> elements of the normal vector through the transformation. Moreover,
> these individual elements were not introduced in advance.
> Page 3, Equation (9): The variable alpha is not described and
> explained
> Page 4, Equation (10): Description of the individual variables is
> missing and, moreover, rho has already been used as the distance
> parameter of the Hesse-normal form
> Page 4, Equation (12): Is epsilon here the same variable as the
> threshold in Section 3.3? Probably not.
> Page 4, Column 2, Line 15: "some dimensions": Which ones and why
> exactly are they chosen? Are they the same ones all the time?
> Page 4, Column 2, Line 20-25: Reference is missing
> Page 4, Column 2, Line 55: Doubled information regarding the
> distance measurement precision
> Page 5, Column 1, Equation (18): Delta t is not introduced and there
> is no indication of how large the time steps are in the simulation.
> Page 5, Column 2, Line 14: Should it be "out" or "our"?
> Page 5, Column 2, Line 27-28: What are the specifications of the
> used IMU with regard to its uncertainty budget?
> Page 6, Figure 1: How are these values to be interpreted and from
> where are they derived? This is unclear.
> Page 8, Column 1, Table 1: What is missing is a classification of
> the values in relation to the expectations / demands...which are,
> however, still missing in advance
> Page 8, Column 1, Line 37-43: At this point, an interpretation of
> the significant second peak in the right-hand diagram in Figure 4
> should be made. This has not been discussed so far.
> Page 8, Column 1, Line 51: "ten scans" means ten individual scan
> lines or 10 epochs or is this identical? What kind of temporal
> offset is there in between and wouldn't a motion model have to be
> taken into account for this or is an identical pose assumed for the
> ten scans?
> Page 8, Column 1, Line 55-56: What could be the cause of this?
> Page 8, Column 2, Line 44: This sentence always applies and should
> not remain here.
> Page 9, Figure 4: The two point clouds in the middle of figure 4 are
> difficult to interpret in terms of their orientation. Could it be an
> option to add a coordinate system?

### 2021-06-28 Latex/rebuttal.txt

> reformulated. -> Split into two sentences
> Page 2, Column 2, Line 15: The term "long stop" is not to be
> interpreted clearly in this context. How is "long" defined in this
> sense in terms of time or space? -> Specified stop is required to find enough points for plane detection

@@

> the first half of the sentence, as reference 19 probably only refers
> to the second part. -> Added todo for Dorit/Andreas as they wrote this
> Page 3, Column 1, Line 23-26: Not all variables were introduced
> accurately -> Introduced missing variables and and clarified rho
> Page 3, Column 1, Line 33-34: Selection of references for this? -> Added plane segmentation sources

@@

> explained -> explained alpha
> Page 4, Equation (10): Description of the individual variables is
> missing and, moreover, rho has already been used as the distance
> parameter of the Hesse-normal form -> replaced rho with zeta, introduced variables

@@

> Page 4, Equation (12): Is epsilon here the same variable as the
> threshold in Section 3.3? Probably not.-> renamed epsilon, clarified difference to sec 3.3

@@

> Page 4, Column 2, Line 15: "some dimensions": Which ones and why
> exactly are they chosen? Are they the same ones all the time? -> chose better example, added todo for Fabi
> Page 4, Column 2, Line 20-25: Reference is missing -> added source

@@

> Page 5, Column 2, Line 27-28: What are the specifications of the
> used IMU with regard to its uncertainty budget? -> added precision of IMU + source
> Page 6, Figure 1: How are these values to be interpreted and from
> where are they derived? This is unclear.-> specified (chosen to still allow plane detection)

@@

> Page 8, Column 1, Table 1: What is missing is a classification of
> the values in relation to the expectations / demands...which are,
> however, still missing in advance -> I don't understand this comment? TODO 

@@

> lines or 10 epochs or is this identical? What kind of temporal
> offset is there in between and wouldn't a motion model have to be
> taken into account for this or is an identical pose assumed for the
> ten scans? -> Specified which scans and that we assuem constant pose
> Page 8, Column 1, Line 55-56: What could be the cause of this?-> specified outlier dependence

@@

> not remain here. -> removed :(
> Page 9, Figure 4: The two point clouds in the middle of figure 4 are
> difficult to interpret in terms of their orientation. Could it be an
> option to add a coordinate system? -> specified in the figure label that lateral images have the same orientation

### 2021-06-28 Latex/main.tex
Changed Author List
Done reviewer 2 additional points corrections

%% Group authors per affiliation:
\author{Fabian Arzberger and Anton Bredenbeck, Jasper Zevering, Dorit Borrmann, Andreas Nüchter}
\address{Informatics VII: Robotics and Telematics,
Julius-Maximilians-University Würzburg, Germany\\
%One contact suffices
e-mail: dorit.borrmann@uni-wuerzburg.de}

@@

\begin{abstract}
Spherical robots are a format that has not been thoroughly explored for the application of mobile mapping. 
In contrast to other designes, it provides some unique advantages. 
Among those is a protective spherical shell that protects internal sensors and actuators from possible harsh environments, as well as an inherent rotation for locomotion that enables measurements in all directions.
Mobile mapping always requires a high-precise pose knowledge to obtain consistent and correct environment maps. 
This is typically done by a combination of external reference sensors such as Global Navigation Satellite System (GNSS) measurements and inertial measurements or by post processing the data and registering the different measurements to each other. 
In indoor environments, the GNSS reference is not an option.
Hence many mobile mapping applications turn to the second option.
An advantage of indoor environments is that human-made environments usually have a certain structure, such as parallel and perpendicular planes.
We propose a registration procedure that exploits this structure by minimizing the distance of measured points to a corresponding plane. 
Further, we evaluate the procedure on a simulated dataset of an ideal corridor and on an experimentally acquired dataset with different motion profiles. 
We show that we nearly reproduce the ground truth for the simulated dataset and improve the average point-to-point distance to a reference scan in the experimental dataset.
The presented algorithms are required to work completely autonomously.
\end{abstract}

>>>>

%% Group authors per affiliation:
\author{Fabian Arzberger, Anton Bredenbeck, Jasper Zevering, Dorit Borrmann, Andreas Nüchter}
\address{Informatics VII: Robotics and Telematics,
Julius-Maximilians-University Würzburg, Germany\\
%One contact suffices
e-mail: dorit.borrmann@uni-wuerzburg.de}

@@

\begin{abstract}
Spherical robots are a format that has not been thoroughly explored for the application of mobile mapping. 
In contrast to other designs, it provides some unique advantages. 
Among those is a spherical shell that protects internal sensors and actuators from possible harsh environments, as well as an inherent rotation for locomotion that enables measurements in all directions.
Mobile mapping always requires a high-precise pose knowledge to obtain consistent and correct environment maps. 
This is typically done by a combination of external reference sensors such as Global Navigation Satellite System (GNSS) measurements and inertial measurements or by coarsely estimating the pose using inertial measurement units (IMUs) and post processing the data by registering the different measurements to each other. 
In indoor environments, the GNSS reference is not an option.
Hence many mobile mapping applications turn to the second option.
An advantage of indoor environments is that human-made environments usually have a certain structure, such as parallel and perpendicular planes.
We propose a registration procedure that exploits this structure by minimizing the distance of measured points to a corresponding plane. 
Further, we evaluate the procedure on a simulated dataset of an ideal corridor and on an experimentally acquired dataset with different motion profiles. 
We show that we nearly reproduce the ground truth for the simulated dataset and improve the average point-to-point distance to a reference scan in the experimental dataset.
The presented algorithms are required to work completely autonomously.
\end{abstract}

### 2021-06-28 Latex/sections/introduction.tex
Done reviewer 2 additional points corrections

This paper proposes to use such a spherical robot for mobile mapping man-made environments.
In such environments, one advantage are architectural shapes following standard conventions arising from tradition or utility, i.e., there are many flat surfaces such as walls, floors, etc. that are sensed.
Exploiting this fact yields more opportunities for registration as point-to-plane correspondences can be used.
The proposed registration method minimizes the distances of each point to its corresponding plane as an objective function.
The method is evaluated on a simulated dataset as well as on experimentally acquired datasets.

>>>>

This paper proposes to use such a spherical robot for mobile mapping man-made environments.
In such environments, one advantage are architectural shapes following standard conventions arising from tradition or utility. In particular, there are many flat surfaces such as walls, floors, etc. that are sensed.
Exploiting this fact yields more opportunities for registration as point-to-plane correspondences can be used.
The proposed registration method minimizes the distances of each point to its corresponding plane as an objective function.
The method is evaluated on a simulated dataset as well as on experimentally acquired datasets.

### 2021-06-28 Latex/sections/realData.tex
Done reviewer 2 additional points corrections

We also tested out algorithm on a real-world dataset that adheres to different motion profiles and laser scanners type with different scanning patterns than the simulated data.

The dataset is collected by a line scanner, in particular a SICK LMS141 industrial scanner, inside a sphere of a diameter of \SI{20}{\centi\meter} that lies on a floating desk, which is air-pressurized, such that the sphere is hovering.
On this floating desk, the sphere can rotate freely about all axis while being fixed in position. 
Hence, in this experiment the optimization space can be reduced to a rotation.
Further, without the motion, the 2D laser cannot obtain a 3D model from the environment, thus requiring registration. 
The sphere is equipped with a low-cost IMU, i.e., a PhidgetSpatial Precision 3/3/3, to estimate the orientation, a battery pack and a raspberry pie for processing.

>>>>

We also tested our algorithm on a real-world dataset that adheres to different motion profiles and laser scanners type with different scanning patterns than the simulated data.

The dataset is collected by a line scanner, in particular a SICK LMS141 industrial scanner, inside a sphere of a diameter of \SI{20}{\centi\meter} that lies on a floating desk, which is air-pressurized, such that the sphere is hovering.
On this floating desk, the sphere can rotate freely about all axis while being fixed in position. 
Hence, in this experiment the optimization space can be reduced to a rotation.
Further, without the motion, the 2D laser cannot obtain a 3D model from the environment, thus requiring registration. 
The sphere is equipped with a low-cost IMU, i.e., a PhidgetSpatial Precision 3/3/3, to estimate the orientation, a battery pack and a raspberry pie for processing.
This IMU provides a precision of \SI{76.3}{\micro g} in linear acceleration, \SI{0.02}{\degree\per\second} in angular velocity about the x and y axis, and \SI{0.013}{\degree\per\second} in angular velocity about the z axis \cite{PhidgetSpatial}.
